Eclipse Che for Fair and Easy Education

### 2019-06-21 che.tex
Added Formalia
added text to competitors and theia

\begin{document}
%%% Mehrere Autoren werden durch \and voneinander getrennt.
%%% Die Fußnote enthält die Adresse sowie eine E-Mail-Adresse.
%%% Das optionale Argument (sofern angegeben) wird für die Kopfzeile verwendet.
\title[Eclipse Che for Education]{Eclipse Che for Fair and Easy Education}
%%%\subtitle{Untertitel / Subtitle} % falls benötigt
\author[Leonhard Applis]
{Leonhard Applis \footnote{Technische Hochschule Georg Simon Ohm, \email{Leonhard.Applis@Protonmail.com}}}
%\startpage{-} % Beginn der Seitenzählung für diesen Beitrag
%\editor{-}    % Namen der Herausgeber
\booktitle{Under Revision for SKILL 2019} % Name des Tagungsband
\year{2019}
%%%\lnidoi{18.18420/provided-by-editor-02} % Falls bekannt
\maketitle

@@

\section{Introduction}
\label{sec:Introduction}
Children look into the clouds and count sheep. 
Developers look into the clouds and check their applications.  
Cloud technologies are already state of the art, enabling global players like Google to run applications on a world-scale.
The market-leaders stocked up their portfolios with  a  variety  of  different  cloud  technologies,  ranging from cloud computing, cloud storage, database-as-a-service or rented authentication. 
Modern software needs to be scalable, self-contained, and should run on any device, as well as in the cloud.  
This trend is also visible in Google searches \ref{fig:digdocker}.

@@

Eclipse Che  can be run  on any  base-technology  on  localhost – this is rather for demonstrations as well as for developers working on the Che-Code. 
When run (locally) on docker, the plugin CheDir enables a portable workspace, 
which can be used on any docker based Che.
\subsection{Technology and Workflow}
\label{subsec:Tec}
A normal IDE is software on a computer which makes programming easier than doing it in a plain text-editor and commandline. 
Common tasks for an IDE are dependency management, debugging, refactoring and auto-completion.
It is important that an IDE is not \textit{required} to develop - Vim can write Java files, the JDK can compile and the JRE can run everything manually from console. 
With that in mind,an IDE is just a tool-stack to make things (a lot) more comfortable – but it also has requirements such as the JDK, the .Jars needed in the classpath etc. as they are only utilized by the IDE.
This stack can be considered a \textit{workspace} as it contains everything required to work, with the IDE making the workspace comfortable to use.
Eclipse Che does not work like a normal IDE. 
Che consists of three main components shown in Figure \ref{fig:cheworkflow}\footnote{source: \url{https://en.wikipedia.org/wiki/Eclipse_Che\#/media/File:Eclipse_Che_-_Workflow.PNG}}.

@@

>>>>

\begin{document}
%%% Mehrere Autoren werden durch \and voneinander getrennt.
%%% Die Fußnote enthält die Adresse sowie eine E-Mail-Adresse.
%%% Das optionale Argument (sofern angegeben) wird für die Kopfzeile verwendet.
\title[Eclipse Che for Education]{Eclipse Che for Fair and Easy Education}
%%%\subtitle{Untertitel / Subtitle} % falls benötigt
\author[Leonhard Applis]
{Leonhard Applis \footnote{Technische Hochschule Georg Simon Ohm, \email{Leonhard.Applis@Protonmail.com}}}
%\startpage{-} % Beginn der Seitenzählung für diesen Beitrag
\editor{Gesellschaft für Informatik}    % Namen der Herausgeber
\booktitle{SKILL 2019} % Name des Tagungsband
%\band{Lecture Note in Informatics (LNI) – Seminars, Gesellschaft für Informatik, Bonn 2019}
\year{2019}
%%%\lnidoi{18.18420/provided-by-editor-02} % Falls bekannt
\maketitle

@@

\section{Introduction}
\label{sec:Introduction}
Children look into the clouds and count sheep. 
Developers look into the clouds and check their applications.  
Cloud technologies are already state of the art, enabling global players to run applications on a world-scale.
The market-leaders stocked up their portfolios with  a  variety  of  different  cloud  technologies,  ranging from cloud computing, cloud storage, database-as-a-service or rented authentication. 
Modern software needs to be scalable, self-contained, and should run on any device, as well as in the cloud.  
This trend is also visible in Google searches \ref{fig:digdocker}.

@@

Eclipse Che  can be run  on any  base-technology  on  localhost – this is rather for demonstrations as well as for developers working on the Che-Code. 
When run (locally) on docker, the plugin CheDir enables a portable workspace, 
which can be used on any docker based Che.

\subsection{Technology and Workflow}
\label{subsec:Tec}
A normal IDE is software on a computer which makes programming easier than doing it in a plain text-editor and commandline. 
Common tasks for an IDE are dependency management, debugging, refactoring and auto-completion.
It is important that an IDE is not \textit{required} to develop - Vim can write Java files, the JDK can compile and the JRE can run everything manually from console. 
With that in mind,an IDE is just a tool-stack to make things (a lot) more comfortable – but it also has requirements such as the JDK, the .Jars needed in the classpath etc. as they are only utilized by the IDE.
This stack can be considered a \textit{workspace} as it contains everything required to work, with the IDE making the workspace comfortable to use.
Eclipse Che does not work like a normal IDE. 
Che consists of three main components shown in Figure \ref{fig:cheworkflow}\footnote{source: \url{https://en.wikipedia.org/wiki/Eclipse_Che\#/media/File:Eclipse_Che_-_Workflow.PNG}}.

@@

Eclipse Che originates from the Eclise-Theia project. 
Theia focussed (only) on the idea of having a remote workspace and access it via browser. 
Che uses Theia and enriches it with idea of capsulation and containerization. 
An alternative to Eclipse Che is Amazons Cloud9\footnote{https://aws.amazon.com/cloud9/}, which is free for students. 
Microsoft is currently working on a similiar solution, the plattform Coder\footnote{https://coder.com/} is on a state similiar to Eclipse-Theia. 
Che is the only completely free and open sourced Cloud-IDE.
